---
title: "Hard Work 3"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
---

## Instructions

1. Study Sections 3.1-3.8 of Chapter 3: "Diagnostics and Remedial Measures."    
<span id=note>(We will study more of Chapter 3 next week.)</span>


2. Attempt and submit at least <span id=points style="padding-left:0px;">{52}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{56}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{62}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{70}</span> gets you {+3} Final Exam Points.</span>

## Reading Points <span id=headpoints>{30} Possible</span>

<div style="padding-left:20px;">

### Section 3.1 <span id=recpoints>{2}</span><span id=report>{ 2/1 }</span>

### Section 3.2 <span id=recpoints>{2}</span><span id=report>{ 2/ 1}</span>

### Section 3.3 <span id=recpoints>{8}</span><span id=report>{8 / 4}</span>

### Section 3.4 <span id=recpoints>{2}</span><span id=report>{ 2/1 }</span>

### Section 3.5 <span id=recpoints>{2}</span><span id=report>{ 2/1 }</span>

### Section 3.6 <span id=recpoints>{6}</span><span id=report>{ 6/ 3}</span>

### Section 3.7 <span id=recpoints>{7}</span><span id=report>{ 7/ 3}</span>

### Section 3.8 <span id=recpoints>{1}</span><span id=report>{ 1/1 }</span>

</div>

## Theory Points <span id=headpoints>{9} Possible</span>

<div style="padding-left:20px;">

### 3.1 <span id=recpoints>{2}</span><span id=report>{ 2/2 }</span>
```{r}
#A residuals stay on the scale that the data is on semi-studentized residual is scaling the data to put on the same scale. to show outliers. 
#B expected value of epsilon compared to the ebar is the mean of e. 
#C error term is the deviation of the observervation to the true term. The residual is the difference between the observered value and the estimated value. 
```

 
### 3.12 <span id=points>{2}</span><span id=report>{ / }</span>

### 3.21 <span id=points>{3}</span><span id=report>{ / }</span>

### 3.23 <span id=points>{2}</span><span id=report>{ / }</span>


</div>


## Application Points <span id=headpoints>{32} Possible</span>

<div style="padding-left:20px;">

<a id=datalink style="font-size:.9em;" target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>

### 3.3 <span id=recpoints>{6}</span><span id=report>{6 / 4}</span>

```{r p33}
# Load the Data:
p3.3 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%203%20Data%20Sets/CH03PR03.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p3.3) <- c("Y","X")
```

```{r}
library(tidyverse)
library(mosaic)
library(alr3)
library(lmtest)
library(onewaytests)
dat <- p3.3
my_lm <- lm(Y~X, data = dat)
#A
dat %>% 
  ggplot(aes(x = X, y = Y))+
  geom_boxplot()
#B
dat %>% 
  ggplot(aes(x = X, y = Y))+
  geom_point()

#C
plot(my_lm$residuals, type = "b")

#D
plot(my_lm$residuals, type = "o")
cor(dat$X, dat$Y)
#E

```

### 3.4 <span id=recpoints>{6}</span><span id=report>{ 6/ 2}</span>

```{r p34}
# Load the Data:
p3.4 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%203%20Data%20Sets/CH03PR04.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p3.4) <- c("Y","X")
```

```{r}
dat1 <- p3.4
lm_my <- lm(Y~X, data = dat1)

#A
dat1 %>% 
  ggplot(aes(x = X, y = Y))+
  geom_point()
#that as x gets bigger y gets bigger as well. I don't see any outlying variables. 

#B
plot(dat1$X, type = "l")

#C
stem(lm_my$residuals)

#E
plot(lm_my$residuals, type = "o")
cor(dat$X, dat$Y)


```


### 3.5 <span id=recpoints>{5}</span><span id=report>{ 5/ 2}</span>

```{r p35}
# Load the Data:
p1.21 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR21.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.21) <- c("Y","X")
```

```{r}
dat2 <- p1.21
my_lm1 <- lm(Y~X, data = dat2)
#A
dat2 %>% 
  ggplot(aes(x = X, y = Y))+
  geom_point()
#Yes it appears to be assymetic. 

#B
plot(dat2$X, type = "l")
#Mostly there is an outlier but it looks pretty asymmetric. The outlier is right in the middle but it helps with the asymmetric look. 

#C
stem(my_lm1$residuals)

#D
```


### 3.6 <span id=points>{5}</span><span id=report>{ / }</span>

```{r p36}
# Load the Data:
p1.22 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### 3.7 <span id=points>{4}</span><span id=report>{ / }</span>

```{r p37}
# Load the Data:
p1.27 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR27.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.27) <- c("Y","X")
```


### 3.8 <span id=points>{3}</span><span id=report>{ / }</span>

```{r p38}
# Load the Data:
p1.28 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```


### 3.13 <span id=recpoints>{3}</span><span id=report>{ 3/ 1}</span>

```{r p313}
# Load the Data:
p1.20 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```

```{r}
dat3 <- p1.20
my_lm2 <- lm(Y~X, data = dat3)

#A 
#The alternative conclusion is that the line does not fit a regression line. 

#B
pureErrorAnova(my_lm2)

#C

```


</div>










 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


<footer>
</footer>



 

 

 

 