---
title: "Hard Work 2 (Part 1)"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---


## Instructions

1. Study Sections 2.1-2.6 of Chapter 2: "Inferences in Regression and Correlation Analysis."    
<span id="note">(Next week we will study Sections 2.7-2.10.)</span>

2. Attempt and submit at least <span id=points style="padding-left:0px;">{47}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{52}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{60}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{67}</span> gets you {+3} Final Exam Points.</span>

<br/>



## Reading Points <span id=headpoints>{23} Possible</span>

### Section 2.1 <span id=recpoints>{6}</span><span id=report>{ A=6 | E=4 }</span>

### Section 2.2 <span id=recpoints>{3}</span><span id=report>{ A=3| E=2
}</span>

### Section 2.3 <span id=recpoints>{1}</span><span id=report>{ A=1 | E=1 }</span>

### Section 2.4 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=3 }</span>

### Section 2.5 <span id=recpoints>{6}</span><span id=report>{ A=6 | E=4 }</span>

### Section 2.6 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=2 }</span>



<br/>




## Theory Points <span id=headpoints>{33} Possible</span>

### Problem 2.1 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>
 
### Problem 2.2 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>
 
### Problem 2.3 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.18 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>
<span id=headnote>Hint: Read page 71</span>
 
### Problem 2.19 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.20 or 2.21 or 2.22 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.33 <span id=recpoints>{3}</span><span id=report>{ A=3| E=1 }</span>

```{r}
#Alternative Hypthosize is that it does not equaly $7.5 thousand. 

#B

#c
#you cannot


```


### Problem 2.51 <span id=points>{2}</span><span id=report>{ A=0 | E=0 }</span>

### Exercise 2.55 <span id=recpoints>{2}</span><span id=report>{ A=2 | E=0 }</span>

```{r}
# summation of Yi = Beta0 + Beta1 * Xi
```


### Exercise 2.57 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Exercise 2.61 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

 

<br/>



## Application Points <span id=headpoints>{53} Possible</span>

<a id=datalink target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>


### Problem 2.1 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.4 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=2 }</span>

```{r p4}
# Load the Data:
p1.19 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")
```

```{r}
mydata <- p1.19

summary(mydata)
 
mylm <- lm(X~Y, data = mydata)
#plot(x=X, y=Y, data = mylm)
#abline(mylm)
coef(mylm, .95)
summary(mylm)
```


### Problem 2.5 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=0 }</span> 

```{r p5}
# Load the Data:
p1.20 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```

```{r}
dat <- p1.20
summary(dat)
 
mylm <- lm(X~Y, data = dat)
#plot(x=X, y=Y, data = mylm)
#abline(mylm)
coef(mylm, .90)
summary(mylm)

```

### Problem 2.7 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span> 

```{r p7}
# Load the Data:
p1.22 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### Problem 2.10 <span id=recpoints>{2}</span><span id=report>{ A=2 | E=2 }</span> 

```{r}
#A Predicction Ionterval
#B Confidence Interval
#C Prediction Interval 
```

### Problem 2.13 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=1 }</span> 

```{r p13}
# Load the Data:
p1.19 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")
```

```{r}
dat1 <- p1.19

summary(dat1)
 
mylm <- lm(X~Y, data = dat1)
plot(X~Y, data = dat1)
#abline(mylm)
coef(mylm, .95)
summary(mylm)


```

### Problem 2.14 <span id=points>{4}</span><span id=report>{ A=0 | E=0 }</span> 

```{r p14}
# Load the Data:
p1.20 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```


### Problem 2.15 <span id=points>{4}</span><span id=report>{ A=0 | E=0 }</span>

```{r p15}
# Load the Data:
p1.21 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR21.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.21) <- c("Y","X")
```


### Problem 2.16 <span id=recpoints>{5}</span><span id=report>{ A=5 | E=2 }</span> 

```{r p16}
# Load the Data:
p1.22 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


```{r}

dat2 <- p1.22
mylm <- lm(X~Y, data = dat2)
plot(X~Y, data = dat2)
#abline(mylm)
predict(mylm, data.frame(Y = 30))
coef(mylm)
summary(mylm)
```

<br />



 

 
 
 
 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


 

 