---
title: "Hard Work 12"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
library(mosaic)
library(car)
library(plotly)
library(reshape2)
library(scatterplot3d)
library(tidyverse)
```

<style>

</style>

## Instructions

1. Study Chapter 14 -- "Logistic Regression, Poisson Regression, and Generalized Linear Models"    

2. Attempt and submit at least <span id=points style="padding-left:0px;">{50}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{66}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{72}</span> gets you {+2} Final Exam Points.</span>    


\


## Reading Points <span id=headpoints>{42} Possible</span>

### Section 14.1 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.2 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.3 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.4 <span id=points>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.5 <span id=points>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.6 <span id=points>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.7 <span id=points>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.8 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Section 14.9 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Section 14.10 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Section 14.11 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Section 14.12 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>

### Section 14.13 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=2 }</span>

### Section 14.14 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span>


\





## Theory Points <span id=headpoints>{6} Possible</span>

### Problem {14.1} <span id=points>{3}</span><span id=report>{ A=3 | E=3 }</span>

The Benoulli Distribution rises just two possibilities "success" or "failure".
P denotes the probability of success and of failure(1-p). p(0)= (1-p) and p(1)=p.

### Problem {14.3} <span id=points>{3}</span><span id=report>{ A=3 | E=3 }</span>

This would not be a great time to use logisitc regression. We want the response variable to work more on an S-Shape. 

## Application Points <span id=headpoints>{20} Possible</span>


### Problem {14.7} <span id=points>{5}</span><span id=report>{ A=5 | E=5 }</span>
```{r}
p14.7 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%2014%20Data%20Sets/CH14PR07.txt", header = FALSE)
colnames(p14.7) <- c("Y","X")

```
A
```{r}
p14.7model <- glm(Y ~ X, data = p14.7, family = binomial)
summary(p14.7model)
```
-0.6000
0.02857
$$
\hat{\pi_i} = \frac{e^{-4.80751 + 0.125 X_i}}{1+e6{-4.810751 + 0.125 X_I}}
$$
B
```{r}
p14.7 %>% 
  ggplot(aes(x = X, y = Y))+
  geom_point()+
  geom_smooth()+
  stat_smooth(method = "glm", method.args = list(family= "binomial"), col = "green")
```

C
```{r}
exp(0.12508)
```
1.133239
Every increase in X by 1 you ODDS of leaving increase your chances by 13%. 
D
```{r}
predict(p14.7model, data.frame(X = 40, type = "response"))
```
0.1956164 

19.56%

E
```{r}
y <- log(0.75/(0.25))
x <- (y + 4.81 / (0.125))
```

It has to increase by 39.58 Dolllars for 75% to cancel their membership. 

### Problem {14.9} <span id=points>{5}</span><span id=report>{ A=5 | E=5 }</span>
```{r}
p14.9 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%2014%20Data%20Sets/CH14PR09.txt", header = FALSE)
colnames(p14.9) <- c("Y","X")

```
A
```{r}
p14.9model <- glm(Y ~ X, data = p14.9, family = binomial)
summary(p14.9model)
```
-0.6000
0.02857
$$
\hat{\pi_i} = \frac{e^{-10.308925 + 0.018920 X_i}}{1+e{-10.308925 + 0.018920 X_I}}
$$
B
```{r}
p14.9 %>% 
  ggplot(aes(x = X, y = Y))+
  geom_point()+
  geom_smooth()+
  stat_smooth(method = "glm", method.args = list(family= "binomial"), col = "green")
```

C
```{r}
exp(0.02857)
```
When you increase by 1 you increase your chances by 2.9%
D
```{r}
predict(p14.9model, data.frame(X = 550, type = "response"))
```
9.6%
E
```{r}
y <- log(0.70/(0.30))
x <- (y + 10.308925 / (0.018920))
print(x)
```
The expected test score of 545.7165.



### Problem {14.13} <span id=points>{5}</span><span id=report>{ A=5 | E=5 }</span>
```{r}
p14.13 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%2014%20Data%20Sets/CH14PR13.txt", header = FALSE)
colnames(p14.13) <- c("Y","X1","X2")

```

A
```{r}
p14.13model <- glm(Y ~ X1 + X2, data = p14.13, family = binomial)
summary(p14.13model)
```
$$
\hat{\pi_i} = \frac{e^{-4.73931 + 0.06773 X_\text{i1} + 0.59863 X_\text{i2}}} {1+e6{-4.73931 + 0.06773 X_\text{i1}}+ 0.59863 X_\text{i2}} 
$$
B

```{r}
exp(0.06773)
exp(0.59863)
```
C
```{r}
predict(p14.13model, data.frame(X1 = 50000, X2 = 3), type = "response")
```

### Problem {14.14} <span id=points>{5}</span><span id=report>{ A=5 | E=5 }</span>
```{r}
p14.14 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%2014%20Data%20Sets/CH14PR14.txt", header = FALSE)
colnames(p14.14) <- c("Y","X1","X2","X3")
```
A
```{r}

p14.14model <- glm(Y ~ X1 + X2 + X3, data = p14.14, family = binomial)
summary(p14.14model)
```
$$
\hat{\pi_i} = \frac{e^{-1.17716 + 0.07279 X_\text{i1} + (-0.09899) X_\text{i2} + 0.43397 X_\text{i3}}} {1+e6{-1.7716 + 0.07279 X_\text{i1}}+ (-0.09899) X_\text{i2} + 0.43397 X_\text{i3}} 
$$



B
```{r}
exp(0.07279)
exp(-0.09899)
exp(0.43397)

```
X1 is a 7.5 % of increase.
X2 is a 10% decrease.
X3 is a 54% increase. 


C
```{r}
predict(p14.14model, data.frame(X1= 55, X2 = 60, X3 = 1), type = "response")
```

The probability of 55 year olds with a health index of 60 to recieive the flu shot is 6.4%. 

<style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}


#rrecpoints {
  font-size:1em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}



#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}


</style>


<footer>
</footer>



 

 

 

 