---
title: "Hard Work 2 (Part 2)"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---


## Instructions

1. Study Sections 2.7-2.10 of Chapter 2: "Inferences in Regression and Correlation Analysis."    

2. Attempt and submit at least <span id=points style="padding-left:0px;">{36}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{40}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{47}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{53}</span> gets you {+3} Final Exam Points.</span>

<br/>



## Reading Points <span id=headpoints>{17} Possible</span>

### Section 2.7 <span id=recpoints>{8}</span><span id=report>{ A=8 | E=4 }</span>

### Section 2.8 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=2 }</span>

### Section 2.9 <span id=recpoints>{3}</span><span id=report>{ A=3 | E=1 }</span>

### Section 2.10 <span id=recpoints>{2}</span><span id=report>{ A=2 | E=1 }</span>


<br/>




## Theory Points <span id=headpoints>{14} Possible</span>

### Problem 2.9 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>
 
### Problem 2.11 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>
 
### Problem 2.12 <span id=points>{1}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.50 <span id=points>{2}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.53 <span id=points>{4}</span><span id=report>{ A=0 | E=0 }</span>

### Problem 2.66 <span id=recpoints>{5}</span><span id=report>{ A=5 | E=5 }</span> 

<span id=note>R-Code Hint: rnorm(5, 0, sqrt(25))</span>

```{r}
library(tidyverse)
dat <- data.frame(x=c(4,8,12,16,20), error=rnorm(5,0,sqrt(25))) %>% 
  mutate(y = 20+4*x+error)

mylm <- lm(y~x, data = dat)
summary(mylm)
predict(mylm, interval = "confidence")
```

```{r}
b <- matrix(NA, 200, 2)
for (i in 1:200){
  dat <- data.frame(x=c(4,8,12,16,20), error=rnorm(5,0,sqrt(25))) %>% 
    mutate(y = 20+4*x+error) 
  my_lm <- lm(y~x, data = dat) 
  b[i,] <- coef(my_lm)
  interval <- predict(my_lm, data.frame(x = 10), interval = "confidence")
}

hist(b[,1])
mean(b[,1])
sd(b[,1])
predict(my_lm, interval = "confidence")

```

<br/>



## Application Points <span id=headpoints>{22} Possible</span>

<a id=datalink target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>

### Problem 2.25 <span id=recpoints>{5}</span><span id=report>{ A=5 | E=3 }</span>

```{r p25}
# Load the Data:
p1.20 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```

```{r}
my_lm <- lm(Y~X,data = p1.20)
summary(my_lm)

anova(my_lm)
#a 1 numerator 43 denomitor df sum sq 76960 & 3416

#b f-value 968.66
#c 31.1233
summary(my_lm)
plot(my_lm)
#d  0.9575 0.9565
```

### Problem 2.26 <span id=recpoints>{4}</span><span id=report>{ A=4 | E=3 }</span>

```{r p26}
# Load the Data:
p1.22 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```

```{r}
my.lm <- lm(Y~X, data = p1.22)
summary(my.lm)
anova(my.lm)

plot(Y~X, data = p1.22)
abline(my.lm)

plot(Y~X, data = p1.22)
abline(my.lm)
abline(h=mean(p1.22$Y))

#c R^2 shows the precentage of data corrilates to the fitted line. 
```

### Problem 2.29 <span id=recpoints>{5}</span><span id=report>{ A=5 | E=4 }</span> 

```{r p29}
# Load the Data:
p1.27 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR27.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.27) <- c("Y","X")
```

```{r}
lm_my  <- lm(Y~X, data = p1.27)
plot(Y~X, data = p1.27)
abline(lm_my)

plot(Y~X, data = p1.27)
abline(lm_my)
abline(h = mean(p1.27$Y))

anova(lm_my)

#



```


### Problem 2.30 <span id=points>{5}</span><span id=report>{ A=0 | E=0 }</span> 

```{r p30}
# Load the Data:
p1.28 <- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```

### Problem 2.32 <span id=points>{3}</span><span id=report>{ A=0 | E=0 }</span> 

```{r p32}
# Load the Data:
p1.28<- read.table("http://users.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```



<br />



 

 
 
 
 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


 

 