---
title: "Personal Regression Application"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
---
```{r}
library(tidyverse)
library(mosaic)
library(janitor)

dat <- read_csv("health_data.csv")
dat <- clean_names(dat) %>% 
  adorn_rounding(digits = 3, rounding = "half to even") %>% 
  select(active_calories_kcal, distance_mi, flights_climbed_count, heart_rate_count_min, resting_calories_kcal) %>% 
  filter(active_calories_kcal, distance_mi, flights_climbed_count, heart_rate_count_min, resting_calories_kcal >= 0 )
  
```

### Pairs Plot and Model Testing
```{r}
pairs(dat, panel = panel.smooth)

model <- lm(active_calories_kcal ~ distance_mi, data = dat)
summary(model)

#model2 <- lm(active_calories_kcal ~ flights_climbed_count, data = dat)
#summary(model2)

pairs(cbind(R=model$res, F = model$fit, dat), panel = panel.smooth)

plot(model)
```


After looking at the pairs plot and the summary table of the model I have elected that the best model that fits this data is the model with the Y as the Active Calories on the Distance in Miles. Now that I have found the right model I want to predict how many calories I will burn if I walk 2 miles a day

```{r}
predict(model, data.frame(distance_mi = 2), interval = "prediction", level = 0.95)
```

Based on the prediction I will burn about 709.0076 calories at 2 miles a day but with a max of 871.56 and a low of 546.45 calories at 2 miles a day. 
<style>

</style>

## Instructions

1. Use regression to help you find meaningful insights about your own life.

    * You could study your spending and earning habits.
    * You could consider your health habits as recorded by your phone or other electronic gadget.
    * You could consider the impacts of social media usage measured by number of posts, time spent, or words written, compared to your success in school each semester.
    * You could weigh your future job opportunities, graduate school, or other options against each other to find a "best choice" for you.
    * You could even take a second attempt at the Project 3 analysis, and follow up with more detail that better reflects your actual vehicle scenario. This would have to differ rather significantly from Project 3 though.

<br />

2. Your work should show breadth and depth of knowledge in the things we have learned this semester. 

## Grading

1. Breadth of Knowledge <span id=points style="padding-left:0px;">{10} Points</span>

    * What percentage of regression concepts from this semester does your analysis demonstrate?

<br />

2. Depth of Knowledge <span id=points style="padding-left:0px;">{10} Points</span>

    * Does your analysis show great expertise in at least a few of the regression topics we have covered this semester? Specifically, you need to demonstrate good ability with: the mathematical model statement, hypothesis testing, confidence or prediction intervals, and transformations.
    
    

<footer>
</footer>



 
 <style>
 #points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#rrecpoints {
  font-size:1em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
 </style>

 

 

 