---
title: "Project 3 -- Predicting Math 325 Final Exam Scores"
author: "Matt Hirschi"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


## Overview

The goal of this project is to come up with a model that accurately predicts final exam scores in Math 325.

The earlier in the semester that your model can be applied, the more useful it becomes. The goal of the prediction is two-fold. First, it gives the students in the course an accurate prediction of how well they are doing knowledge-wise in the course. Second, it allows the teacher a way to identify students that are struggling early on in hopes of helping them improve their final performance.

## Step 1. Find your Data

Use the `Math325` dataset that is provided (in I-Learn) for this project.

```{r}
library(tidyverse)
library(mosaic)
library(car)
library(janitor)
dat <- read_csv("Math325.csv")
```


## Step 2. Model the Data

Use good model selection strategies to develop a "best" model for predicting the data. Defend your choice of the model with supporting p-values, supporting information criterion (like $R^2_a$, $AIC$, or $BIC$), and useful graphics (like scatterplots, added variable plots and diagnostic plots).

```{r}
dat1 <- dat %>% 
  select(FinalExam, SkillsQuizW1, SkillsQuizW2, SkillsQuizW3,SkillsQuizW4, SkillsQuizW5, SkillsQuizW6,Project1, Analysis1, Analysis2) %>% 
  mutate(Total = SkillsQuizW1 + SkillsQuizW2 + SkillsQuizW3 + SkillsQuizW4 + SkillsQuizW5 + SkillsQuizW6) %>% 
  mutate(Total_1 = Analysis1 + Analysis2)

pairs(dat1, panel = panel.smooth)

#best model I found
model <- lm(FinalExam ~ Total +  I(Total) + Analysis2 + Total:Analysis2 + I(Total^2):Analysis2, data = dat1)
summary(model)

model1 <- lm(FinalExam ~ Total + Analysis2 + Total:Analysis2, data = dat1)
summary(model1)

model2 <- lm(FinalExam ~ SkillsQuizW1 + I(SkillsQuizW1^2) + Analysis2 + SkillsQuizW1:Analysis2 + I(SkillsQuizW1^2):Analysis2, data = dat1)
summary(model2)
model3 <- lm(FinalExam ~ Total +  I(Total^2) + Total_1 + Total:Total_1 + I(Total^2):Total_1, data = dat1)
summary(model)

plot(model3, which = 1:2)
qqPlot(model)
```

## Step 3. Describe your Strategy

Interpret your regression model and describe it in a way that is simple and intuiative. 


## Grading

You will be graded on two things.

1. How well you apply the regression principles we have learned thus far this semester. (Think Projects 1 and 2.) 

2. How well you interpret your results and describe your "buying and selling" strategy.








<style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


<footer>
</footer>



 

 

 

 